Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-30 manuscript/manuscript.tex
Changes in manuscript

For this reason we developed a density-based discretization algorithm that divides the tesseroid on the radius at which the \emph{maximum variation} of the density function takes place, only if a inequation that relates this \emph{maximum variation} with a predefined delta ratio $\delta$ holds.
Therefore the number of subdivisions is indirectly controlled by this delta ratio $\delta$, and thus the accuracy of the computation.

Because there is no direct relation between the values of $D$ and $\delta$ and the error of the computation, we had to empirically determine the minimum value of $D$ and the maximum value of $\delta$ that produce an acceptable accuracy for each gravity field.

The distance-size ratio determinations have been made through the comparison of the numerical approximations with the analytical solutions for the a spherical shell with variable density, which had to be analytically obtained.
From the wide range of possible density variations, we've chosen a linear, an exponential and a discontinuous density functions.
These comparisons have been made without applying the density-based discretization algorithm in order to isolate the other one.
The tests over the first two functions have shown that a value of $D$ equal to 1, 2 and 8 must be used in the calculation of the gravity potential, its gradient components and the components of the Marussi tensor, respectively, in order to achieve an accuracy bellow 0.1\%.
On the other hand we have found a limitation of this algorithm working on its own in case of highly varying exponential functions and in some cases of discontinuous density.

Nevertheless, the density-based discretization algorithm have shown that a value of $\delta = 0.2$ (together with the previously obtained default values of $D$) guarantees a good accuracy on those cases on which the modified adaptive discretization algorithm does not achieve it on its own.

>>>>

For this reason we developed a density-based discretization algorithm that divides the tesseroid on the radius at which the \emph{maximum variation} of the density function takes place, only if a certain inequation that relates this \emph{maximum variation} with a predefined delta ratio $\delta$ holds.
Therefore the number of subdivisions is indirectly controlled by this delta ratio $\delta$, and thus the accuracy of the computation.

Because there is no direct relation between the values assigned to $D$ and $\delta$ and the error of the computation, we had to empirically determine the minimum value of $D$ and the maximum value of $\delta$ that produce an acceptable accuracy for each gravity field.

The distance-size ratio determinations have been made through the comparison of the numerical approximations with the analytical solutions for the a spherical shell with variable density, which had to be analytically obtained.
From the wide range of possible density variations, we've chosen a linear, an exponential and a discontinuous density functions.
These comparisons have been made without applying the density-based discretization algorithm in order to isolate the former one.
The tests over the first two functions have shown that values of $D$ equal to 1, 2 and 8 for the calculation of the gravity potential, its gradient and the Marussi tensor components, respectively, produce an accuracy of 0.1\% or better.
On the other hand, the algorithm on its own does not guarantee this amount of accuracy in case of highly varying exponential functions or discontinuous densities.

We have performed similar tests for the density-based discretization algorithm comparing the numerical model with the analytical solutions for a spherical shell with various exponential densities: from a low varying to a high varying one.
Each comparison was made for different values of $\delta$, keeping the default values of $D$ previously obtained.
This tests have shown that a value of $\delta = 0.2$ guarantees an accuracy of 0.1\% or better on every case, while the same results can be obtained performing this tests with the discontinuous density function.
